### 2013-05-16 Docs/initial_models/initial_models.tex
some updates

We have found that for the best performance, the \maestro\
initialization procedure should be given model data with the same
resolution as the base state resolution, $\Delta r$.  For planar
problems, $\Delta r = \Delta x$.  For multilevel planar problems, we
use $\Delta r$ equal to $\Delta x$ at the finest resolution.  For
spherical problems we set $\Delta r = \Delta x/\mathtt{drdxfac}$.  We
generate our initial model either analytically or from raw data,
$\rho^{\raw}, T^{\raw}, p^{\raw}$, and $X^{\raw}$.  Here is the raw
data file for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt test\_convect} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/model\_6.e8.raw} \nonumber \\
{\tt spherical\_heat} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/sorted\_xrb.raw} \nonumber
\end{eqnarray}

We use a fortran subroutine
to interpolate the raw data, yielding the model data, $\rho^{\model},
T^{\model}, p^{\model}$, and $X^{\model}$.  The fortran subroutine
then uses an iterative procedure to modify the model data so that it
is thermodynamically consistent with the {\tt MAESTRO} equation of
state (EOS), and also satisfies our chosen hydrostatic equilibrium
(HSE) discretization,
\begin{equation}
\frac{p_r - p_{r-1}}{\Delta r} = \frac{\rho_r + \rho_{r-1}}{2}g_{r-\myhalf},\label{HSE Discretization}
\end{equation}
to a user defined tolerance.  Here are the fortran subroutines for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & {\tt initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/init\_1d.f90} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt initial\_models/spherical/init\_1d.f90} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/init\_1d.f90} \nonumber
\end{eqnarray}
The model data is not generated at run-time - it must be generated in
advance of running any \maestro\ examples.  The inputs file should point
to the file containing the model data.

>>>>

We have found that for the best performance, the \maestro\
initialization procedure should be given model data with the same
resolution as the base state resolution, $\Delta r$.  For planar
problems, $\Delta r = \Delta x$.  For multilevel planar problems, we
use $\Delta r$ equal to $\Delta x$ at the finest resolution.  For
spherical problems we set $\Delta r = \Delta x/\mathtt{drdxfac}$.  We
generate our initial model either analytically or from raw data,
$\rho^{\raw}, T^{\raw}, p^{\raw}$, and $X^{\raw}$.  Here is the raw
data file for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt test\_convect} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt model\_6.e8.raw} \nonumber \\
{\tt spherical\_heat} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \\
\end{eqnarray}

We use a fortran subroutine
to interpolate the raw data, yielding the model data, $\rho^{\model},
T^{\model}, p^{\model}$, and $X^{\model}$.  The fortran subroutine
then uses an iterative procedure to modify the model data so that it
is thermodynamically consistent with the \maestro\ equation of
state (EOS), and also satisfies our chosen hydrostatic equilibrium
(HSE) discretization,
\begin{equation}
\frac{p_r - p_{r-1}}{\Delta r} = \frac{\rho_r + \rho_{r-1}}{2}g_{r-\myhalf},\label{HSE Discretization}
\end{equation}
to a user defined tolerance.  Here are the fortran subroutines for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & {\tt Util/initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt Util/initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt wdconvect} & \rightarrow & none\footnotemark \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt Util/initial\_models/spherical/init\_1d.f90} \nonumber \\
\end{eqnarray}
\footnotetext{the original model routines are not distributed, but the {\tt Util/initial\_models/spherical/init\_1d.f90} routines can work as a simple substitute.}
The model data is not generated at run-time---it must be generated in
advance of running any \maestro\ examples.  The inputs file should point
to the file containing the model data.
